---
title: "Meet the team"
toc: false
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
library(knitr)
library(quarto)
```

# Paul Corballis
**Lab Director**

:::: {.grid} 

:::  {.g-col-8}
Paul summary
:::

::: {.g-col-4}
![](images/default_user.svg)
:::

::::

---

```{r, pressure, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
studentscsv <- read_csv("students_csv.csv")
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# Run this and use output in qmd file

#cat(paste0("`r randDispOrd <- sample(nrow(studentscsv)) `\n"))

for (i in 1:nrow(studentscsv)) {
    if (i == 1) {cat(paste0("`r randDispOrd <- sample(nrow(studentscsv)) `\n"))
}
  # output name and title
  cat(paste0("# `r studentscsv$name[randDispOrd[",i,"]] `\n"))
  cat(paste0("**`r studentscsv$position[randDispOrd[",i,"]] `**\n\n"))
  # output the summary in a grid format
  cat(":::: {.grid}\n\n")
  if (i %% 2 == 0) {
    cat("::: {.g-col-5}\n")
    cat(paste0("![](images/`r studentscsv$image[randDispOrd[",i,"]] `){width=100% height=auto}\n"))
  } else {
    cat("::: {.g-col-7}\n")
    cat("`r studentscsv$summary[randDispOrd[",i,"]] `", "\n")
  }
  cat(":::\n\n")
  if (i %% 2 == 0) {
    cat("::: {.g-col-7}\n")
    cat("`r studentscsv$summary[randDispOrd[",i,"]] `", "\n")
  } else {
    cat("::: {.g-col-5}\n")
    cat(paste0("![](images/`r studentscsv$image[randDispOrd[",i,"]] `){width=100% height=auto}\n"))
  }
  cat(":::\n\n")
  cat("::::\n\n")
  cat("---\n\n")
}
```

`r randDispOrd <- sample(nrow(studentscsv)) `
# `r studentscsv$name[randDispOrd[1]] `
**`r studentscsv$position[randDispOrd[1]] `**

:::: {.grid}

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 1 ]] ` 
:::

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[1]] `){width=100% height=auto}
:::

::::

---

# `r studentscsv$name[randDispOrd[2]] `
**`r studentscsv$position[randDispOrd[2]] `**

:::: {.grid}

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[2]] `){width=100% height=auto}
:::

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 2 ]] ` 
:::

::::

---

# `r studentscsv$name[randDispOrd[3]] `
**`r studentscsv$position[randDispOrd[3]] `**

:::: {.grid}

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 3 ]] ` 
:::

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[3]] `){width=100% height=auto}
:::

::::

---

# `r studentscsv$name[randDispOrd[4]] `
**`r studentscsv$position[randDispOrd[4]] `**

:::: {.grid}

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[4]] `){width=100% height=auto}
:::

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 4 ]] ` 
:::

::::

---

# `r studentscsv$name[randDispOrd[5]] `
**`r studentscsv$position[randDispOrd[5]] `**

:::: {.grid}

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 5 ]] ` 
:::

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[5]] `){width=100% height=auto}
:::

::::

---

# `r studentscsv$name[randDispOrd[6]] `
**`r studentscsv$position[randDispOrd[6]] `**

:::: {.grid}

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[6]] `){width=100% height=auto}
:::

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 6 ]] ` 
:::

::::

---

# `r studentscsv$name[randDispOrd[7]] `
**`r studentscsv$position[randDispOrd[7]] `**

:::: {.grid}

::: {.g-col-7}
`r studentscsv$summary[randDispOrd[ 7 ]] ` 
:::

::: {.g-col-5}
![](images/`r studentscsv$image[randDispOrd[7]] `){width=100% height=auto}
:::

::::

---